\LARGE \bf Bringing robotics into formal education \\ using the Thymio open source hardware robot

### 2016-04-14 paper_ram.tex
Attempt to improve section on problems of opne-source hardware

\subsection{Problems of open-source projects}

@@

The very specific structure of an open project has also drawbacks. 
Asked about problems met in their project (Fig.~\ref{fig:problems}), the participants to our survey mention the management of the community, the evolution of the project, the efforts in documentation, production and distribution and the limited resources.
There are here two kinds of problems: one of management of people, the other in the development of the project after the first design.
The management of the project seems a recurrent problem and is related to the nature of this type of structure, mainly very flat and built on academic people with engineering background. 
More than 62\% of the answers to our survey report about projects that are managed by the founder of the initiative and not by the most expert in the field or by a manager, which is perhaps not the best objective choice.
It is indeed very difficult to evolve from a phase where the engineering is the core of the project, to a new phase where communication and management play an increasing role.
This problem is deeply connected with the one of acquiring sustained funding for the project, in order to build a professional team able to support the product.
The same holds for several other factors, like the efforts in documentation, production and distribution of the product. 
Also here there is a change of activity from the very creative and appealing design phase, to a phase of documentation and, in some cases, production and distribution which is not at all the same type of activity and requires different skills.
This shift requires extra efforts and motivation, which are often missing, especially for activities like documentation that are not appreciated by engineers.
In general many respondents to our survey identified the evolution of the project as a general problematic issue, which summarizes the several aspects mentioned above.

>>>>

\subsection{Problems of open-source hardware projects}

@@

The very specific structure of an open-source hardware project has also drawbacks. 
Asked about problems met in their project (Fig.~\ref{fig:problems}), the participants to our survey mention the management of the community, the evolution of the project, the efforts in documentation, production and distribution and the limited resources.
These problems are mainly caused by the mismatch between the conditions of the initial phase of the project, and the needs of long term sustainability.
Initially, these projects are created by academic people with engineering background, typically in a flat structure.
However, long term sustainability requirements are closer to the ones of a successful startup, and involve communication, marketing, and professional management in order to acquire sustained funding.
Yet, 62\% of the participants to our survey report projects that are managed by the founder of the initiative, who might not be the best person to lead such a structure.
This differs from open-source software, because initiating hardware production requires the investment of a large amount of money, and modifying hardware is much slower than modifying software.
Moreover, in the case of robotics, although software plays a critical part, the perception of the product is highly centered on the hardware.
Therefore, in open hardware projects, there is a structural conflict between the open-source ideals and the concrete financial and logistic constraints.

% There are here two kinds of problems: one of management of people, the other in the development of the project after the first design.
% The management of the project seems a recurrent problem and is related to the nature of this type of structure, mainly very flat and built on academic people with engineering background. 
% More than 62\% of the answers to our survey report about projects that are managed by the founder of the initiative and not by the most expert in the field or by a manager, which is perhaps not the best objective choice.
% It is indeed very difficult to evolve from a phase where the engineering is the core of the project, to a new phase where communication and management play an increasing role.
% This problem is deeply connected with the one of acquiring sustained funding for the project, in order to build a professional team able to support the product.
% The same holds for several other factors, like the efforts in documentation, production and distribution of the product. 
% Also here there is a change of activity from the very creative and appealing design phase, to a phase of documentation and, in some cases, production and distribution which is not at all the same type of activity and requires different skills.
% This shift requires extra efforts and motivation, which are often missing, especially for activities like documentation that are not appreciated by engineers.
% In general many respondents to our survey identified the evolution of the project as a general problematic issue, which summarizes the several aspects mentioned above.
